Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-08 tensor/draft/draft-tensor-op.tex
[tensor] Add posterior predictions for sc910SPTT5 to draft
[draft-tensor-op.tex] updated IV.D

We start with the scenario of the combination of tensor and scalar couplings
$\wilson{S,S',P,P',T,T5, 10,10'}$ \todo{(extend this discussion right away to include
also $\wilson{10,\, 10'}$)}, i.e. the combination of the preceding
two sections. In this scenario there are only small changes on the bounds, in fact
they tend to be even more stringent, because tensor and scalar couplings
can contribute to $F_H^{\mu}$ only constructively --- see \refeq{eq:FH-dependence}.
As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
constraints on $\wilson{T,\, T5}$. Furthermore we find that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts. In this case, the constraints are even a bit tighter and strong correlations
arise as before among real parts of $\wilson{i}$ and $\wilson{i'}$ for $i = S,P$,
and in addition similarly among their imaginary parts.
\todo{Check this with EOS}

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $T,\,T5,\,9,\,10,$
  & $S^{(')},\,P^{(')},\,9^{(')},\,10^{(')}$
  & $S^{(')},P^{(')},\,T,\,T5,\,9^{(')},10^{(')}$
  \\
  \hline \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
  & 1
  & SM
  & $[-1,\, 1]$
  & \eos{???}
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}

>>>>

The most general fit of complex-valued tensorial and scalar couplings 
$\wilson{S,S',P,P',T,T5}$ in combination with complex-valued vectorial couplings
$\wilson{9,\,9',\,10,\, 10'}$ --- i.e. the combination of \refsec{sec:tensor}
and \refsec{sec:scalar} with same prior ranges --- does not yield very different
bounds. The changes are only small and in fact the bounds tend to be even more
stringent, because tensor and scalar couplings can contribute to $F_H^{\mu}$
only constructively --- see \refeq{eq:FH-dependence}.
As before ${\cal B}$'s of $B\to K^{(*)}\bar\mu\mu$ help to strengthen the
constraints on $\wilson{T,\, T5}$. This demonstrates that even in the case
of complex-valued couplings the data is able to constrain all real and imaginary
parts.

@@

\begin{table*}
  \renewcommand{\arraystretch}{1.5}
  %\resizebox{\textwidth}{!}{
  \begin{tabular}{cc|c|ccc}
  \hline
    observable
  & $q^2$-bin [GeV$^2$]
  & SM
  & $T,\,T5,\,9,\,10,$
  & $S^{(')},\,P^{(')},\,9^{(')},\,10^{(')}$
  & $S^{(')},P^{(')},\,T,\,T5,\,9^{(')},10^{(')}$
  \\
  \hline \hline
  \multirow{2}{*}{$\tau_{B^0} \times J_{6c}$}
  & $[1.1,\, 6]$
  & $\simeq 0$
  & $(0.7_{-2.1}^{+1.7}) \cdot 10^{-9\;}$
  & $(0.0_{-2.1}^{+2.2}) \cdot 10^{-10}$
  & \eos{$( 0.71_{-1.98}^{+0.52}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $\simeq 0$
  & $(2.1_{-6.2}^{+5.1}) \cdot 10^{-10}$
  & $(0.7_{-6.6}^{+5.4}) \cdot 10^{-11}$
  & \eos{$(-0.25_{-0.23}^{+0.72}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1c} + J_{2c})$}
  & $[1.1,\, 6]$
  & $(3.54_{-0.66}^{+0.65}) \cdot 10^{-9\;}$
  & $(5.0_{-1.9}^{+1.7}) \cdot 10^{-9\;}$
  & $(2.9_{-0.5}^{+0.4}) \cdot 10^{-9\;}$
  & \eos{$(3.23_{-1.31}^{+2.36}) \cdot 10^{-21}$}
  \\
  & $[15,\, 19]$
  & $(1.72_{-0.16}^{+0.16}) \cdot 10^{-10}$
  & $(4.7_{-2.6}^{+3.3}) \cdot 10^{-9\;}$
  & $(1.9_{-0.7}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(7.28_{-3.29}^{+5.17}) \cdot 10^{-21}$}
  \\
  \hline
  \multirow{2}{*}{$\tau_{B^0} \times (J_{1s} - 3 J_{2s})$}
  & $[1.1,\, 6]$
  & $(2.98_{-0.54}^{+0.63}) \cdot 10^{-10}$
  & $(1.9_{-1.1}^{+1.4}) \cdot 10^{-8\;}$
  & $(4.9_{-1.4}^{+1.6}) \cdot 10^{-10}$
  & \eos{$(2.00_{-0.97}^{+1.03}) \cdot 10^{-20}$}
  \\
  & $[15,\, 19]$
  & $(1.12_{-0.10}^{+0.10}) \cdot 10^{-10}$
  & $(7.1_{-3.8}^{+5.6}) \cdot 10^{-9\;}$
  & $(1.4_{-0.4}^{+0.3}) \cdot 10^{-10}$
  & \eos{$(9.29_{-4.54}^{+3.86}) \cdot 10^{-21}$}
  \\
  \hline \hline
  \multicolumn{2}{c|}{$A_{\Delta \Gamma}(B_s \to \bar\mu\mu)$}
  & 1
  & SM
  & $[-1,\, 1]$
  & $[-1,\, 1]$
  \\
  \hline
  \end{tabular}
%}
  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:postdictions}
     The 68\% probability intervals of not yet measured angular observables in
     $B^0\to K^{*0}\bar\mu\mu$ integrated over $q^2$ bins at low- and high-$q^2$
     for several new physics scenarios respecting all the considered experimental
     constraints. The SM prior predictives are given too, where ``$\simeq 0$''
     indicates zero in the considered
     approximation, see text for more explanations.
  }
\end{table*}
